% #############################################################################
% Agradecimentos / Acknowledgments
% !TEX root = ../main.tex
% #############################################################################

First of all, I would like to thank my advisor, Prof. João Nuno Oliveira Silva, for accepting the challenge and for his indications and guidance during the development of the project. 

Secondly, I would like to thank EDP, namely Diana Pinto for inviting me to join this project, and Eng. Francisco Maria Santos and Eng. Luís Resende Martins for all the help and support they provided me during the development of this work, being essential for the success of this experience.

Thirdly, I would like to thank FCUL, namely the researcher Dimitri Boutov and Prof. Rodrigo Amaro da Silva for facilitating my access to meteorological data and weather data.

I would also like to thank all my family for all the support, in particular my sister Inês Bogalho, my mother Patrícia Reis, my grandmother Tomélia Reis, my father João Bogalho and my grandfather Raul Guerreiro, for always being present and for all the unconditional love and understanding. To all my Family, thank you.

I would like to thank my friends, in particular those who were with me during my journey at the Instituto Superior Técnico, Maria Siopa, Carlos Pires, João Rosa and Luís Rodriguez, and also my lifelong friends Diogo Pires and José Maria Inglês. Last but not least, I would like to thank Carolina Caramelo for all the motivation and encouragement throughout all these months of work.